Supplementary material for 'The complex network of trophic interactions in a subAntarctic Marine Protected Area

### 2023-04-26 MS_ToSubmit/SupMaterial.Rmd
Updates co-authors

# Load data
load("../data/cleaned-data_jan23.rda")

@@

# Load packages
library(knitr)
library(dplyr)
library(kableExtra)

# Load data
load("../data/cleaned-data_jan23.rda")
load("../data/foodweb-data_jan23.rda")

@@

# Load data
load("../results/summary_results_jan23.rda")

>>>>

# Load data
load("../data/cleaned-data_apr23.rda")

@@

# Load packages
library(knitr)
library(dplyr)
library(kableExtra)
library(stringr)

# Load data
load("../data/cleaned-data_apr23.rda")
load("../data/foodweb-data_apr23.rda")

@@

# Load data
load("../results/summary_results_apr23.rda")
